LCS Tool — An Algorithmic Introduction to Lagrangian Coherent Structures

### 2014-02-16 main.tex
Remove unused newcommand FIXME
Correct notation used for strainlines and stretchlines

\newcommand{\FIXME}[1]{\\\fbox{FIXME: #1}\\}

@@

\subsection{Hyperbolic LCS}
Hyperbolic LCSs are trajectories of the eigenvector fields $\boldsymbol \xi_{1,2}$. Repelling hyperbolic LCSs, denoted strainlines, are obtained as solutions of the differential equation
\begin{equation}
\boldsymbol r_1' = \boldsymbol \xi_1(\boldsymbol r),
\label{eq:strainline}
\end{equation}
and attracting hyperbolic LCSs, denoted stretchlines, are obtained as a solution of the differential equation
\[
\boldsymbol r_2' = \boldsymbol \xi_2(\boldsymbol r).
\]
A normal perturbation to the strainline segment $\boldsymbol r_1'$ grows under the flow map by a factor $\lambda_2$, i.e., fluid elements are repelled at that rate in the normal direction. Equivalently, a normal perturbation to the stretchline segment $\boldsymbol r_2'$ shrinks by a factor $\lambda_1$ and fluid elements are attracted.

Similarly to elliptic LCS, hyperbolic LCS are also based on a variational principle, in this case for the Lagrangian shear
\[
p(s) = \frac{\langle \boldsymbol r'(s), D(\boldsymbol r(s)) \boldsymbol r'(s)\rangle}{\sqrt{\langle \boldsymbol r'(s), C(\boldsymbol r(s)) \boldsymbol r'(s)\rangle \langle \boldsymbol r'(s), \boldsymbol r'(s)\rangle}}
\]
where
\[
D(\boldsymbol x_0) = \frac12[C(\boldsymbol x_0) \Omega - \Omega C(\boldsymbol x_0)], \quad \Omega = \begin{pmatrix}0&-1\\1&0\end{pmatrix}.
\]
The first variation of the average Lagrangian shear along a hyperbolic LCS vanishes
\[
P(\gamma) = \frac{1}{\sigma} \int_0^\sigma p(s) \text{d}s,
\]
\[
\delta P(\gamma) = 0.
\]
They are one type of shear-less LCS. For details of the derivation of hyperbolic LCS, see \cite{farazmand13:_shearless}.

>>>>

@@

\subsection{Hyperbolic LCS}
Hyperbolic LCSs are trajectories of the eigenvector fields $\boldsymbol \xi_{1,2}$. Repelling hyperbolic LCSs, denoted strainlines, are obtained as solutions of the differential equation
\begin{equation}
\boldsymbol r' = \boldsymbol \xi_1(\boldsymbol r),
\label{eq:strainline}
\end{equation}
and attracting hyperbolic LCSs, denoted stretchlines, are obtained as a solution of the differential equation
\[
\boldsymbol r' = \boldsymbol \xi_2(\boldsymbol r).
\]
A normal perturbation a strainline segment grows under the flow map by a factor $\lambda_2$, i.e., fluid elements are repelled at that rate in the normal direction. Equivalently, a normal perturbation a stretchline segment shrinks by a factor $\lambda_1$ and fluid elements are attracted.

Similarly to elliptic LCS, hyperbolic LCS are also based on a variational principle, in this case for the Lagrangian shear
\[
p(s) = \frac{\langle \boldsymbol r'(s), D(\boldsymbol r(s)) \boldsymbol r'(s)\rangle}{\sqrt{\langle \boldsymbol r'(s), C(\boldsymbol r(s)) \boldsymbol r'(s)\rangle \langle \boldsymbol r'(s), \boldsymbol r'(s)\rangle}}
\]
where
\[
D(\boldsymbol x_0) = \frac12[C(\boldsymbol x_0) \Omega - \Omega C(\boldsymbol x_0)], \quad \Omega = \begin{pmatrix}0&-1\\1&0\end{pmatrix}.
\]
The first variation of the average Lagrangian shear along a hyperbolic LCS vanishes
\[
P(\gamma) = \frac{1}{\sigma} \int_0^\sigma p(s) \text{d}s,
\]
\[
\delta P(\gamma) = 0.
\]
They are one type of shearless LCS. For details of the derivation of hyperbolic LCS, see \cite{farazmand13:_shearless}.
